---
title: "DataAnalytics_Assignment"
author: "Manisha sharma"
date: "August 3, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
##To research distribution of income among different gender based on different industries.


### Retrieve the data

```{r }

incomeData <- read.csv("D:\\695\\week11\\income.csv")
str(incomeData)

incomeData <- na.omit(incomeData)

```
### To check association between quantative data

```{r }
chisq.test(incomeData$M_weekly,incomeData$F_weekly)
chisq.test(incomeData$All_workers,incomeData$All_weekly)
chisq.test(incomeData$M_workers,incomeData$F_workers)

```
###Exploratory Data Analysis

```{r }


library(ggplot2)

library(caret)

# considering 5 industries based on preference
indData <- subset(incomeData, incomeData$Industry == "Management" | incomeData$Industry =="Engineering"| incomeData$Industry == "Science")
histogram(indData$Industry)

ggplot(incomeData, aes(x = incomeData$Industry, y = incomeData$All_workers)) + geom_point()

```
#Explain what type of regression you will choose and why
### Logistic regression can be used. Dependant variable in this dataset is industry which is categorical variable

```{r }
plot(incomeData$Industry,incomeData$All_weekly)
```






Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
